%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Gabriel Ramirez}{April 9, 1983}  % Your name and date of birth or subtitle

\noindent\href{mailto:luga.ramirez@gmail.com}{luga.ramirez@gmail.com}
\ifdefined\nophone\else\bull \textsmaller{+}31 626-957064\fi
\bull \href{https://www.linkedin.com/in/lugaramirez/}{lugaramirez} \textit{(LinkedIn)}
\bull \href{https://github.com/lugaramirez}{lugaramirez} \textit{(GitHub)}
\bull Marius Bauerstraat 30-B4
\bull Amsterdam, 1062AR
\bull The Netherlands % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

Backend and Platform Engineer with over 10 years of experience designing distributed systems, leading engineering teams, and delivering software across e-commerce, fintech, healthcare, and public safety domains. Proven ability to simplify complex architectures through Domain-Driven Design and clean code principles. \textit{Areas of expertise include:}

\vspace{-1em} % Reduce whitespace after the Summary heading and the two-column content
\begin{multicols}{2}  % Start a two-column layout
{\bodytext{
  \begin{itemize}[noitemsep,nolistsep]
    \item Software architecture and engineering.
    \item Agile software development.
    \item IaaS technologies.
    \item CI/CD tools.
    \item Electrical and electronics engineering.
    \item Hardware and embedded software design.
    \item Data center infrastructure design.
    \item Network design.
    \item Leadership.
  \end{itemize}
}}
\end{multicols}

\spacedhrule{-1em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://bol.com}{bol.}}
{\textsc{Utrecht, The Netherlands}} {

\headedsubsection % Job title entry for the current employer
{Software Engineer}
{Nov '23 -- Present}
{\bodytext{\textbf{Key Contributions:}
\begin{itemize}
  \item \textbf{Developing and maintaining backend services at scale} (20M+ users, 95k+ req/s combined mobile and web) across Go, Java, Kotlin, and Python, including the company's edge router, GraphQL connectors, and a legacy monolith being migrated to a microfrontend architecture.
  \item \textbf{Leading the migration of login handling from the monolith to an event-based login handler,} enabling other teams to add post-login actions such as anonymous-to-authenticated wish list merging.
  \item \textbf{Active member of a 4-person company-wide quality community,} driving adoption of testing and code quality practices across a multi-language engineering organization.
  \item \textbf{Leading the definition of quality constraints and configurations for \acr{AI}-assisted code generation} (Claude) across the company.
\end{itemize}
}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://quin.md/nl}{Quin}}
{\textsc{Amsterdam, The Netherlands}} {
{\bodytext{Recruited as Tech Lead for the newly created integration team; later promoted to Tech Lead of the platform team, where the team restructured the entire backend through Domain-Driven Design.}}

\headedsubsection % Job title entry for the current employer
{Tech Lead}
{Sep '21 -- Oct '23}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Defined and maintained shared backend libraries} adopted across all engineering teams.
  \item \textbf{Standardized backend development workflows} including Git processes, code review practices, and \acr{CI/CD} pipelines.
  \item \textbf{Led a 3-person team in consolidating 70+ microservices into a single event-driven modular monolith} with 5 bounded domains and 3 anti-corruption layer services, applying Domain-Driven Design throughout.
  \item \textbf{Reduced annual infrastructure costs from \$2M+ to under \$300K} (85\%+ savings), accelerated deployments from quarterly to every merge to main, and cut developer onboarding time from nearly a year to days by aligning the architecture with standard Spring Boot practices.
\end{itemize}
}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://backbase.com/}{Backbase}}
{\textsc{Amsterdam, The Netherlands}} {
{\bodytext{Recruited as a Backend trainer for Backbase's core banking platform; promoted to the R\&D department to develop ''Digital Sales,'' a product enabling bank customer onboarding with automated identity verification, document signing, and notification integrations. }}

\headedsubsection
{Backend Engineer}
{May '20 -- Aug '21}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Architected a connector library template for third-party \acr{API} integrations} (identity verification, \acr{SMS}/email, document signing); personally built 5 connectors, grew to 12 with the team, and the template enabled 50+ connectors after departure.
  \item \textbf{Automated \acr{CI/CD} pipelines to achieve zero-touch releases,} shifting bug detection to build time and reducing re-releases from twice weekly to once per quarter. Product served 5 banking clients.
\end{itemize}
}}

\headedsubsection
{Backend Trainer}
{Jan '20 -- May '20}
{\bodytext{Delivered 3 week-long training sessions on Backbase's core banking platform, training approximately 30 client engineers before the role pivoted due to the global pandemic.}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://swnat.com/}{Software Natura}}
{\textsc{Asuncion, Paraguay}} {
{\bodytext{Software consultancy providing development services to international clients.}}

\headedsubsection
{Software Engineer}
{Feb '17 -- Dec '19}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Led a 7-person consulting team delivering full-stack solutions for Dennis Kirk,} the second-largest American specialized powersports retailer (185k+ parts catalog), collaborating with 5 US-based developers.
  \item \textbf{Developed a C-based Linux kernel module} bridging a legacy Java/Struts call center application to a \acr{COBOL} mainframe, then reimplemented the call center as a Spring Boot + Angular modular monolith with domain-driven boundaries.
  \item \textbf{Built a stock prediction application} using Spring Framework and Angular.
\end{itemize}
}}

\headedsubsection
{\acr{QA} Engineer}
{May '16 -- Jan '17}
{\bodytext{Enforced code quality standards for elumen, a 100k+ line legacy \acr{CRM} monolith serving American community colleges, within a 50-developer team. Grew test coverage from zero to 60\%, shifting bug detection from weeks of end-user feedback to build-time catches by developers.}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Santco \acr{SRL}}
{\textsc{Asuncion, Paraguay}} {
{\bodytext{Software company serving high-profile Paraguayan clients in cattle trading, logistics, and manufacturing.}}

\headedsubsection
{Software Engineer \& Team Lead}
{Nov '14 -- Mar '16}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Implemented Agile development using Scrum} for a team of up to 8 developers building full-stack applications in \acr{PHP} and jQuery.
  \item \textbf{Delivered 4 process-automation applications} on CakePHP and Google Cloud for Paraguay's leading cattle auction house, largest logistics company, and top leather manufacturer --- enabling, for example, the auction house to increase bidding events from weekly to every two days.
\end{itemize}
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.technoma.com.py/}{Technoma \acr{SACI}}}
{\textsc{Asuncion, Paraguay}} {

\headedsubsection
{Field Engineer}
{Mar '10 -- Jul '12}
{\bodytext{\textbf{Key Contributions:}
\begin{itemize}
  \item \textbf{Designed and supervised network deployments across 500+ sites} for banking clients with nationwide branch networks.
  \item \textbf{Led the largest deployment of 200 branches} with 1,000+ NUC terminals and customer-facing printing services including documents, forms, and reports.
\end{itemize}
}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://www.cba.com.py/}{\acr{CBA} \acr{SA}}}
{\textsc{Asuncion, Paraguay}} {

\headedsubsection
{Technology Consultant}
{Mar '11 -- Oct '11}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Established the virtualization and resource allocation stack} using Citrix XenServer, consolidating infrastructure for 15 clients into a shared, on-demand provisioning model.
\end{itemize}
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Paraguayan Ministry of Interior}
{\textsc{Asuncion, Paraguay}} {
{\bodytext{Recruited to design the nationwide Center of Security and Emergencies (\acr{CSE}) for the National Police, Paraguay's 911-equivalent emergency services system.}}

\headedsubsection
{Technology Consultant}
{Mar '10 -- Mar '11}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Designed the physical network and data center infrastructure} for a \$500M+ nationwide resilient optical network spanning Paraguay's major metropolitan areas, supporting tens of thousands of street cameras and coordinated dispatch of police, fire, and ambulance services in real time.
  \end{itemize}
  
}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.universidadcatolica.edu.py/}{Catholic University of Asuncion}}
{\textsc{Asuncion, Paraguay}} {

\headedsubsection
{Junior Researcher}
{Oct '07 -- Apr '10}
{\bodytext{\textbf{Key Contributions:} 
\begin{itemize}
  \item \textbf{Defined the hardware platform for the ''CompuBus'' research project} in a 5-person engineering team, developing embedded software in C and C++ on microcontrollers and small-factor computers, including Linux kernel-level communication modules. Delivered a working prototype deployed with a bus company.
\end{itemize}
  
}}

\headedsubsection
{IT Manager}
{Oct '05 -- Oct '07}
{\bodytext{\textbf{Key Contributions:}
\begin{itemize}
  \item \textbf{Managed approximately 30 internet-facing servers} and 4 computer labs totaling over 200 workstations.
  \item \textbf{Automated lab maintenance,} reducing end-of-semester rebuild time from weeks to hours per weekend, and converted manual server updates to fully unattended automated deployments.
\end{itemize}
}}

}

%------------------------------------------------

\begin{center}
\textit{Please refer to \href{http://www.linkedin.com/in/lugaramirez}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
\end{center}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{University of Leuven}
{\textsc{Leuven, Belgium}} {

\headedsubsection % Job title entry for the current employer
{Masters degree in Nanoscience and Nanotechnology}
{2012 -- 2014}
{\bodytext{Area of interest: Bionanotechnology.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Catholic University of Asuncion}
{\textsc{Asuncion, Paraguay}} {

\headedsubsection % Job title entry for the current employer
{Electrical Engineering \textnormal{(discontinued)}}
{2007 -- 2010} {}

\headedsubsection % Job title entry for the current employer
{Bachelors in Electrical Engineering}
{2002 -- 2006} {}
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection
{Languages:}
{Java, Kotlin, Go, Python, C, C++, JavaScript, \acr{PHP}, \acr{SQL}.}

\inlineheadsection
{Frameworks \& Libraries:}
{Spring Boot, Netflix \acr{OSS}, CakePHP, jQuery, Angular, React.}

\inlineheadsection
{Infrastructure \& DevOps:}
{\acr{AWS}, Azure, Google Cloud, Terraform, Docker, Kubernetes, Jenkins, SonarQube, GitLab \acr{CI/CD}, GitHub Actions, NGINX, Apache, Tomcat, Postgres\acr{SQL}, My\acr{SQL}, \acr{SQL}Server.}

\inlineheadsection
{Methodologies:}
{Agile, Scrum, Domain-Driven Design, Clean Architecture, Microservices.}

\inlineheadsection
{Natural languages:}
{Spanish \textit{(native)}, Guarani \textit{(native)}, English \textit{(full professional proficiency)}, German \textit{(limited working proficiency)}, French \textit{(elementary proficiency)}.}

%------------------------------------------------

\end{document}
